### 2022-12-15 paper.tex
E & H

    f(r)=e^{(p/2)r}[C_+e^{i\sqrt{k-(p/2)^2}r}+C_-e^{-i\sqrt{k-(p/2)^2}r}],

@@

    f(r,t)=e^{(p/2)r}[C_+e^{i(+\sqrt{(\omega/c)-(p/2)^2}r-\omega t)}+C_-e^{i(-\sqrt{(\omega/c)-(p/2)^2}r-\omega t)}],

@@

@@

    f(r,t)=e^{\int(p/2)\d r}[C_+e^{i(+\int\sqrt{(\omega/c)-(p/2)^2}\d r-\omega t)}+C_-e^{i(-\int\sqrt{(\omega/c)-(p/2)^2}\d r-\omega t)}].

@@

>>>>

    f(r)=e^{(p/2)r}[C_+e^{i\sqrt{k^2-(p/2)^2}r}+C_-e^{-i\sqrt{k^2-(p/2)^2}r}],

@@

    f(r,t)=e^{(p/2)r}[C_+e^{i(+\sqrt{(\omega/c)^2-(p/2)^2}r-\omega t)}+C_-e^{i(-\sqrt{(\omega/c)^2-(p/2)^2}r-\omega t)}],

@@

\begin{equation}\label{solution}
    f(r,t)=e^{\int(p/2)\d r}[C_+e^{i(+\int\sqrt{(\omega/c)^2-(p/2)^2}\d r-\omega t)}+C_-e^{i(-\int\sqrt{(\omega/c)^2-(p/2)^2}\d r-\omega t)}],

@@

    f(r,t)=e^{\int O(p)\d r}[C_+e^{i(+\int[(\omega/c)^2+O(p^2)]\d r-\omega t)}+C_-e^{i(+\int[(\omega/c)^2+O(p^2)]\d r-\omega t)}].

@@

If $p$ is small, \eqref{solution} can be approximated to
    f(r,t)=e^{\int(p/2)\d r}[C_+e^{i(+\int(\omega/c)\d r-\omega t)}+C_-e^{i(-\int(\omega/c)\d r-\omega t)}],
then wave of $\vec{E}$ and $\vec{H}$ will approximately arrive Earth at the same time, and also $rE \propto e^{\int(\frac{\d}{\d r}(\ln\mu_{\text{G}})/2)\d r} \propto \mu_{\text{G}}^{1/2}$, $rH\propto e^{\int(\frac{\d}{\d r}(\ln\varepsilon_{\text{G}})/2)\d r} \propto \varepsilon_{\text{G}}^{1/2}$.
